Distributional State Aggregation

### 2020-02-17 minutia/paper/paper.tex
paper updated with Freedman-Diaconis

\title{Adversarial State Aggregation}

@@

    In this work, we scrutinize state-of-the-art deep RL algorithms resiliency to environment parameters alterations
    and then introduced our approach to overcome those. Then a guarantee of performance to these attacks is introduced.

@@

    \section{State Aggregation}
    Value function approximation alleviates the computational hurdle of a large state-space problem.
    We introduce an approximate policy iteration method to solve an aggregate problem.
    State aggregation is an approximation approach to make a problem more tractable by a reduction in dimensionality in
    state space \footnote{aggregation in action space although is possible, has less significance comparatively.}.
    State aggregation, in particular, is a parametric feature-based approximation where the features are membership
    functions of 0-1 form.
    Aggregation groups similar states together, so called representative states, which lets the \textit{aggregate}
    problem to be solved by an exact method.
    The computed value function from the exact solution of the aggregate problem can be then used in the original
    problem.

@@

    \section{Method}
    For the sake of clarity, we elaborate on some preliminary definitions here to have a consistent set of notations
    to the end of this paper. We use model-free LSPI and LSTDQ \citep{Lagoudakis2003} to update and
    evaluate the policy of actions, respectively. CRAAM, on the other hand, as a exact method tries to approximate
    the value function by dynamic programming optimization.

@@

    \subsection{Aggregation}
    Find the best policy then find optimal number of buckets.
    Train the agent and retrieve the best policy then by running the agent with the best policy \textit{generate}
    samples.
    These collected samples are not based on a random policy but the best trained policy (baseline).
    Then we can test our hypothesis on the collected samples to see how discretization affect another trained agent.
    One way to measure the effect of discretization is average reward received by the trained agent.

    \subsection{Adversarial attacks}
    The designed attack may have different levels of access to the underlying training policy which have motivated
    the community to classify adversarial attacks into two distinct categories, namely \textit{white-box} or
    \textit{black-box} attacks. White-box attacks illustrating the scenario in which the... Adversarial attacks fall
    in either one of the following categories based upon the stage, which in the adversary perturbs the model:
    \begin{itemize}
        \item Train time: Data poisoning.
        \item Evaluation time: Adversarial examples.
        \item Deploy time: Black-box attacks.
    \end{itemize}

    \subsection{Objective}
    The aggregate problem is stochastic even if the original problem is deterministic. Once we lay out the aggregate
    problem framework we can solve the problem by any exact methods either value- or policy-space solutions.

    The ultimate goal is deceiving the model either in choosing the worst possible action in an RL task or misclassifying an input in a classification task in a way which is not perceptible for unaided eye. In terms of a Markovian RL task we show how minimum set of worst-case actions are needed to result in the minimum final reward. We try to show that the model is not robust to other configuration of each benchmarks with different dynamics.

    The main goal of adversarial training and examples can be expressed briefly in form of the following equation:
    %    \begin{equation}
    %        \begin{aligned}
    %            & \underset{\theta}{\min}
    %            & & \sum_{x,y \in S} \underset{\delta \in \Delta}{\max}
    %            & & & \textbb{Loss}(x + \delta, y; \theta)
    %        \end{aligned}
    %    \end{equation}

@@

    Our implementation uses Deep Q-Network (DQN)\cite{Mnih2015} as the policy optimizer. OpenAI Gym \cite{Brockman2016} is the testbed in the benchmarks in this paper. In training phase, models are trained in the environment. Online methods such as DQN learn by interacting directly in the environment, however, CRAAM

    % \begin{figure}
    %     \centering
    %     \includegraphics[width=1\columnwidth]{minutia/cartpole-v1_batchsize-32_episodes-100_full-step.png}
    %     \caption{Average reward of DQN training to 100 episodes in cartpole.}
    %     \label{fig:my_label}
    % \end{figure}

>>>>

\title{Distributional State Aggregation}

@@

@@

    \section{State Aggregation}
    Value function approximation alleviates the computational hurdle of a large state-space problem.
    We introduce an approximate policy iteration method to solve an aggregate problem.
    State aggregation is an approximation approach to make a problem more tractable by a reduction in dimensionality in
    state space \footnote{aggre
    gation in action space although is possible, has less significance comparatively.}.
    State aggregation, in particular, is a parametric feature-based approximation where the features are membership
    functions of 0-1 form.
    Aggregation groups similar states together, so called representative states, which lets the \textit{aggregate}
    problem to be solved by an exact method.
    The computed value function from the exact solution of the aggregate problem can be then used in the original
    problem.

@@

    \section{Method}
    Splitting the observations into neighborhoods of similar observations is one way to interpret an aggregation
    problem.
    Inspired by histograms and the statistics behind finding the proper number of bins for a given distribution, we
    build our proposal on top of such basics.
    Finding proper number of bins for a given distribution could be calculated by Freedman-Diaconis rule. As the rule
    states:

    \begin{equation}
        \text { Bin width }=2 \frac{\operatorname{IQR}(x)}{\sqrt[3]{n}}
    \end{equation}

    where n is number of observations and IQR is the interquartile range of data.

    For the sake of clarity, we elaborate on some preliminary definitions here to have a consistent set of notations
    to the end of this paper. We use model-free LSPI and LSTDQ \citep{Lagoudakis2003} to update and
    evaluate the policy of actions, respectively.

@@

    The aggregate problem is stochastic even if the original problem is deterministic.
    Once we lay out the aggregate problem framework we can solve the problem by any exact methods either value- or
    policy-space solutions.

@@
